---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# krikinton

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## About

krikinton is an rJava wrapper of [WorksApplications/kintoki](https://github.com/WorksApplications/kintoki) (a port of the CaboCha to Java).

:heavy_exclamation_mark: This package is quite heavy (> 270MB) because of including some binary files!!

## System Requirements

- Java (>= 1.8.0)

## Usage

```{r}
# remotes::install_github("paithiov909/krikinton")
krikinton::kintoki(c(
  "アニメは1人で作ってるんじゃないんだよ！",
  "アニメ制作はチームワークなんだ！"
))
```

## Licenses

Distributed under the MIT license.

This software includes works licensed under [Apache License, Version2.0](http://www.apache.org/licenses/LICENSE-2.0.html).

## Disclaimers

This software is re-distributing model files originally included in [CaboCha](https://taku910.github.io/cabocha/). However, any of MIT license, Apache License, LGPL, and new BSD license are NOT applied to these models.
 
> 付属のモデルファイル(model 以下のファイル)にはBSDライセンス は適用されません。BSDライセンス は, 付属のプログラムや学習ツールのソース・コード, ドキュメントのみに適用されます。
> 
> 付属のモデルファイルは, 株式会社毎日新聞社の御厚意により 配布されている毎日新聞記事CD-ROM版を基に学習, 作成されたものです。付属のモデルファイルは, 毎日新聞データ使用許諾に関する覚書に記載の利用条件内で その使用及び, 複製，改変，頒布が認められます. そのため配布しているモデルをそのままの形で使うことは, 研究目的, 個人利用に限られます. 誤解ないように言っておくと, これは, CaboCha の利用が研究目的に限定されていることを意味しません。 ご自身で用意なさったコーパスを基に, 独自にモデルを学習, 作成した場合は研究目的以外の利用が可能です。
> 
> 奈良先端科学技術大学院大学ならびに工藤 拓は, CaboCha のプログラム 及び付属のモデルファイルの保証, および特定目的の適合性の保証を含め いかなる保証をも行うものではなく， CaboCha のプログラム 及び付属のモデルを使用，複製，改変，頒布により生じた損害や賠償等については， 法律上の根拠を問わず一切責任を負いません. ご注意ください。
> 
> 将来的には, 著作権やライセンス上の問題から, モデルファイルとプログラムを分割 して配布する予定です。

As referred here, you can use these model files for only research/private use with your own responsibility. For commercial use, you must prepare your original model files so as to use this software.

